\bf Estimating the number of clusters using cross-validation

### 2019-01-11 JCGS-R2/cvclust.tex
caption setting 1

\begin{figure}[H]
\centering
\includegraphics[width=5.5in, height=3.3in]{main_code/demo/bench/setting1/Facet.pdf}
\caption{Performance as correlation increases.}
\label{fig:setting1}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=5.5in, height=3.3in]{main_code/demo/bench/setting1/Facet.pdf}
\caption{Setting 1 performance as correlation increases, faceted by estimation
    method. For each estimate method, the subplot shows the proportion of
    replicates in which estimated number of clusters agrees with the truth
    versus the correlation between dimensions,~$\rho$. Gabriel
    cross-validation performance degrades under moderate correlation, but
    the correlation-corrected version performs well across all values of
    $\rho$.}
\label{fig:setting1}
\end{figure}
